Barneby Lives!

### 2023-06-16 scripts/Barneby_Lives.Rmd
distAZE customizef for, but now wrap first step within function

```{r}
sites <- data.frame(
  longitude_dd = runif(15, min = -120, max = -100), 
  latitude_dd = runif(15, min = 35, max = 48)
  ) %>% 
  st_as_sf(coords = c('longitude_dd', 'latitude_dd'))

places <- st_read('../geodata/places/places.shp')

head(places)
```

@@

  locality <- sf::st_drop_geometry(x)
  locality <- locality[1, 'Locality']

  focal <- places_data[grep(locality, places_data$ID), ]
  if(nrow(focal) > 1){
    union_loc <- sf::st_union(x) |> sf::st_point_on_surface()
    focal <- focal[sf::st_nearest_feature(union_loc, focal),]
  }

  location_from <- sf::st_centroid(focal)

  location_from <- sf::st_transform(location_from, 5070)
  x_planar <- sf::st_transform(x, 5070)
  distances <- sf::st_distance(location_from, x_planar, which = 'Euclidean')

@@

  distances <- data.frame(
    st_drop_geometry(x),
    Distance = round(as.numeric(distances / 1609.34), 1),
    Azimuth = round(as.numeric(azy), 0),
    geometry = x[,'geometry']
  )

@@

>>>>

```{r}
sites <- data.frame(
  longitude_dd = runif(15, min = -120, max = -100), 
  latitude_dd = runif(15, min = 35, max = 48)
  ) %>% 
  st_as_sf(coords = c('longitude_dd', 'latitude_dd'), crs = 4326)

places <- st_read('../geodata/places/places.shp')
nf <- st_nearest_feature(sites, places)

sites <- sites %>%
  mutate(st_drop_geometry(places[nf, 'ID']), .before = geometry)

@@

  locality <- sf::st_drop_geometry(x)
  locality <- locality[1, 'ID']

  focal <- places_data[grep(locality, places_data$ID), ]
  location_from <- sf::st_centroid(focal)

  location_from <- sf::st_transform(location_from, 5070)
  x_planar <- sf::st_transform(x, 5070)
  distances <- sf::st_distance(location_from, x_planar, which = 'Euclidean')
  place <- data.frame('Place' =  st_drop_geometry(places_data[x$ID, 'fetr_nm']))

@@

  distances <- data.frame(
    st_drop_geometry(x),
    Distance = round(as.numeric(distances / 1609.34), -1),
    Azimuth = round(as.numeric(azy), 0),
    Place = place
  )  %>% 
    dplyr::mutate(Site = if_else(
      Distance < 100, paste('At', fetr_nm, '.'),
      paste0(Distance, 'm', ' at ', Azimuth, '° from ', fetr_nm, '.')),
      Site = stringr::str_replace(Site, '\\..$', '.')) %>% 
    dplyr::select(-any_of(c('Distance', 'Azimuth', 'Place', 'ID', 'fetr_nm')))

  out <- dplyr::bind_cols(x, distances) %>% 
    dplyr::relocate(Site, .before = geometry) %>% 
    dplyr::select(-any_of(c('ID')))

@@

test <- distAZE(sites, places)
